### 2017-03-19 article/article.tex
Minor changes on tables
Filled holdout tables
Done with experiment result tables
Worked on Tables

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | }
				\hline
				\multicolumn{3}{ | c | }{Holdout $2/3,1/3$} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	 	& Tasa de Error \\ \cline{3-3}
				 													&  														& $S_0$  \\ \hline
				\multirow{2}{*}{Labor} 		& J48 												& 0 \\ \cline{2-3}
																	& JRIP												&	0	\\ \hline
				\multirow{2}{*}{Soybean} 	& J48 												& 0 \\ \cline{2-3}
																	& JRIP												&	0	\\ \hline
				\multirow{2}{*}{Vote} 		& J48 												& 0 \\ \cline{2-3}
																	& JRIP												&	0	\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | c | c | }
				\hline
				\multicolumn{5}{ | c | }{Holdout $2/3,1/3$ Repetido} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	 	& \multicolumn{3}{ c |}{Tasa de Error} \\ \cline{3-5}
				 													&  														& Semilla 1	& Semilla 2	& Semilla 3 \\ \hline
				\multirow{2}{*}{Labor} 		& J48 												& 0 				& 0 				& 0 				\\ \cline{2-5}
																	& JRIP												&	0 				& 0 				& 0 				\\ \hline
				\multirow{2}{*}{Soybean} 	& J48 												& 0 				& 0 				& 0 				\\ \cline{2-5}
																	& JRIP												&	0 				& 0 				& 0					\\ \hline
				\multirow{2}{*}{Vote} 		& J48 												& 0 				& 0 				& 0 				\\ \cline{2-5}
																	& JRIP												&	0 				& 0 				& 0					\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | }
				\hline
				\multicolumn{3}{ | c | }{Validación Cruzada} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	 	& Tasa de Error \\ \cline{3-3}
																	&  														& $S_0$  \\ \hline
				\multirow{2}{*}{Labor} 		& J48 												& 0 \\ \cline{2-3}
																	& JRIP												&	0	\\ \hline
				\multirow{2}{*}{Soybean} 	& J48 												& 0 \\ \cline{2-3}
																	& JRIP												&	0	\\ \hline
				\multirow{2}{*}{Vote} 		& J48 												& 0 \\ \cline{2-3}
																	& JRIP												&	0	\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | c | c | }
				\hline
				\multicolumn{5}{ | c | }{Validación Cruzada Repetida} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	 	& \multicolumn{3}{ c |}{Tasa de Error} \\ \cline{3-5}
				 													&  														& Semilla 1	& Semilla 2	& Semilla 3 \\ \hline
				\multirow{2}{*}{Labor} 		& J48 												& 0 				& 0 				& 0 				\\ \cline{2-5}
																	& JRIP												&	0 				& 0 				& 0 				\\ \hline
				\multirow{2}{*}{Soybean} 	& J48 												& 0 				& 0 				& 0 				\\ \cline{2-5}
																	& JRIP												&	0 				& 0 				& 0					\\ \hline
				\multirow{2}{*}{Vote} 		& J48 												& 0 				& 0 				& 0 				\\ \cline{2-5}
																	& JRIP												&	0 				& 0 				& 0					\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c || c | c | c | c |}
			\hline
			Algoritmo	&	Holdout & Holdout Repetido 	& Validación Cruzada 	& Validación Cruzada Repetida \\ \hline \hline
			J48				&	0				&	0									&	0										&	0														\\ \hline
			JRIP			& 0				&	0									&	0										&	0														\\
			\hline
			\end{tabular}
			\caption{}
			\label{}

		\end{table}
%-----------------------------
%	Bibliographic references
%-----------------------------
	\nocite{garciparedes:machine-learning-hypothesis-evaluation}
	\nocite{subject:taa}
	\nocite{tool:weka}
  \bibliographystyle{alpha}
  \bibliography{bib/misc}

>>>>

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | }
				\hline
				\multicolumn{3}{ | c | }{Holdout $2/3,1/3$} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	 	& Tasa de Error 		\\ \cline{3-3}
				 													&  														& $\text{Semilla}_1$\\ \hline
				\multirow{2}{*}{Labor} 		& J48 												& $0.105263$ 				\\ \cline{2-3}
																	& JRIP												&	$0.105263$					\\ \hline
				\multirow{2}{*}{Soybean} 	& J48 												& $0.094828$ 					\\ \cline{2-3}
																	& JRIP												&	$0.086207$					\\ \hline
				\multirow{2}{*}{Vote} 		& J48 												& $0.027027$ 					\\ \cline{2-3}
																	& JRIP												&	$0.033784$					\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | c | c | }
				\hline
				\multicolumn{5}{ | c | }{Holdout $2/3,1/3$ Repetido} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	 	& \multicolumn{3}{ c |}{Tasa de Error} \\ \cline{3-5}
				 													&  														& $\text{Semilla}_2$	& $\text{Semilla}_3$	& $\text{Semilla}_4$ \\ \hline
				\multirow{2}{*}{Labor} 		& J48 												& $0.157895$ & $0.315789$ & $0.105263$ \\ \cline{2-5}
																	& JRIP												&	$0.157895$ & $0.210526$ & $0.105263$ \\ \hline
				\multirow{2}{*}{Soybean} 	& J48 												& $0.112069$ & $0.107759$ & $0.137931$ \\ \cline{2-5}
																	& JRIP												&	$0.077586$ & $0.116379$ & $0.073276$	\\ \hline
				\multirow{2}{*}{Vote} 		& J48 												& $0.081081$ & $0.054054$ & $0.060811$	\\ \cline{2-5}
																	& JRIP												&	$0.054054$ & $0.047297$ & $0.047297$	\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | }
				\hline
				\multicolumn{3}{ | c | }{Validación Cruzada} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	 	& Tasa de Error 		\\ \cline{3-3}
																	&  														& $\text{Semilla}_1$\\ \hline
				\multirow{2}{*}{Labor} 		& J48 												& $0.263158$ 				\\ \cline{2-3}
																	& JRIP												&	$0.228070$					\\ \hline
				\multirow{2}{*}{Soybean} 	& J48 												& $0.084919$ 					\\ \cline{2-3}
																	& JRIP												&	$0.077599$					\\ \hline
				\multirow{2}{*}{Vote} 		& J48 												& $0.036782$ 					\\ \cline{2-3}
																	& JRIP												&	$0.045977$					\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c | c | c | c | c | }
				\hline
				\multicolumn{5}{ | c | }{Validación Cruzada Repetida} \\ \hline
				\multirow{2}{*}{Datos}		&\multirow{2}{*}{Algoritmo}	& \multicolumn{3}{ c |}{Tasa de Error} \\ \cline{3-5}
				 													&  													& $\text{Semilla}_2$	& $\text{Semilla}_3$	& $\text{Semilla}_4$ \\ \hline
				\multirow{2}{*}{Labor} 		& J48 											& $0.263158$ & $0.263158$ & $0.245614$ \\ \cline{2-5}
																	& JRIP											&	$0.140351$ & $0.157895$ & $0.157895$ \\ \hline
				\multirow{2}{*}{Soybean} 	& J48 											& $0.098097$ & $0.090776$ & $0.079063$ 	\\ \cline{2-5}
																	& JRIP											&	$0.086384$ & $0.068814$ & $0.081991$	\\ \hline
				\multirow{2}{*}{Vote} 		& J48 											& $0.032184$ & $0.036782$ & $0.034483$ 	\\ \cline{2-5}
																	& JRIP											&	$0.043678$ & $0.041379$ & $0.03908$		\\
				\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

@@

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c || c | c | c | c |}
			\hline
			\multicolumn{5}{ | c | }{Conjunto de Datos: Labor} \\ \hline
			Algoritmo	&	Holdout 		& Holdout Repetido 	& Validación Cruzada 	& Validación Cruzada Repetida \\ \hline \hline
			J48				&	$0.105263$	&	0									&	$0.263158$					&	0														\\ \hline
			JRIP			& $0.105263$	&	0									&	$0.228070$					&	0														\\
			\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c || c | c | c | c |}
			\hline
			\multicolumn{5}{ | c | }{Conjunto de Datos: Soybean} \\ \hline
			Algoritmo	&	Holdout 		& Holdout Repetido 	& Validación Cruzada 	& Validación Cruzada Repetida \\ \hline \hline
			J48				&	$0.094828$	&	0									&	$0.084919$					&	0														\\ \hline
			JRIP			& $0.086207$	&	0									&	$0.077599$					&	0														\\
			\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

		\begin{table}[h]
			\centering
			\begin{tabular}{ | c || c | c | c | c |}
			\hline
			\multicolumn{5}{ | c | }{Conjunto de Datos: Vote} \\ \hline
			Algoritmo	&	Holdout 		& Holdout Repetido 	& Validación Cruzada 	& Validación Cruzada Repetida \\ \hline \hline
			J48				&	$0.027027$	&	0									&	$0.036782$ 					&	0														\\ \hline
			JRIP			&	$0.033784$	&	0									&	$0.045977$					&	0														\\
			\hline
			\end{tabular}
			\caption{}
			\label{}
		\end{table}

%-----------------------------
%	Bibliographic references
%-----------------------------
	\nocite{garciparedes:machine-learning-hypothesis-evaluation}
	\nocite{subject:taa}
	\nocite{tool:weka}
  \bibliographystyle{alpha}
  \bibliography{bib/misc}
